Pillar 1 - Sequential Pattern Mining

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code for d_transactions$taken_PF_HL

@@

```{r join_d_df}
# helper function
join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID"))
join_d_transcript <- function(df) df %>% left_join(d_transcript, by = c("Course ID"))
```

@@

  # Exclude 
  filter(
    Type != "Mandatory",  # (i) mandatory courses e.g. COR, CAP, etc
    ! Letters %in% c(
      "SKI", "PRO",       # (ii) skills & projects (taken by majority of students)
      "SAS", "SAH", "SAC" # (iii) courses of semester abroad (uninformative)
      )
    ) %>%

  # Join with transcripts
  select(
    - Period
    ) %>%
  join_d_transcript %>%

  # Identifying sequenceID
  rename(
    sequenceID = `Student ID`
    ) %>%

  # Identifying evenID
  mutate(
    Period  = substr(Period, 1, 1),
    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
    ) %>%

  # Identifying itemID
  mutate(
    PF = case_when(
      Grade <  pass_grade ~ "fail",
      Grade >= pass_grade ~ "pass"
      ),
    HL = case_when(
      Grade <  high_grade ~ "low",
      Grade >= high_grade ~ "high"
      ),

    item    = `Course ID`,
    item_PF = paste(item, PF, sep = "_"),
    item_HL = paste(item, HL, sep = "_")
    )
```

>>>>

# Set up

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID"))
join_d_transcript <- function(df) df %>% left_join(d_transcript, by = c("Course ID"))

paste_ <- function(...) paste(..., sep = "_")
```

@@

@@

  # Exclude courses taken by majority of students (uninformative)
  filter(
    Type != "Mandatory",
    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
    ) %>%

  # Join with transcripts
  select(- Period) %>% # remove Period to avoid duplicates
  join_d_transcript %>%

  # sequenceID and event ID
  rename(
    sequenceID = `Student ID`,
    eventID = time
    ) %>%

  # itemID
  mutate(
    item    = `Course ID`,
    item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
    item_PF = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
    )
```
